Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-08 src/article.tex
Spell check

The scaffolder algorithm reads through the scaffolder file parsing. Each entry
is then converted to corresponding nucleotide sequence by fetching from the
FASTA file and then performing any designated sequence trimming or reverse
complenting. Each of the sequence entries are then joined into a continuous
single super-sequence and returned to the console output. \pb

>>>>

The scaffolder algorithm reads through the scaffolder file parsing. Each entry
is then converted to corresponding nucleotide sequence by fetching from the
FASTA file and then performing any designated sequence trimming or reverse
complementing. Each of the sequence entries are then joined into a continuous
single super-sequence and returned to the console output. \pb
